Semi-supervised author disambiguation of scientific publications

### 2015-07-15 paper.tex
abstract

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is difficult because (i) an author may use different spellings,
variants or synonyms across her career and/or (ii) distinct authors may share
the same name. Among solutions ot this problem, digital libraries are
increasingly offering tools for authors to manually curate their publications
and claim which ones are theirs. Indirectly, these tools allow for the
inexpensive collection of large annotated training data, which can be further
leveraged to build an automated disambiguation system generalizing to
unlabelled publications. In this context, we propose a semi-supervised machine
learning disambiguation solution in the case large and partially annotated
databases of scientific publications. We describe how this annotated data can
be used at several stages of disambiguation, to learn an accurate classifier
for identifying corefering authors, to guide the clustering of scientific
publications by distinct authors and finally to match the resulting clusters
with existing profiles. Evaluation is carried out on a real-world database of 1
million manual annotations and demonstrates the very good accuracy of the
proposed solution. In particular, our analysis of parameters and features
reveal that... \glnote{To be completed with actual results.}

>>>>

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is often difficult because (i) an author may use different spellings,
variants or synonyms across her career and/or (ii) distinct authors may share
the same name. Among solutions ot this problem, digital libraries are
increasingly offering tools for authors to manually curate their publications
and claim which ones are theirs. Indirectly, these tools allow for the
inexpensive collection of large annotated training data, which can be further
leveraged to build an automated disambiguation system capable of inferring
features or patterns for identifying publications written by a same person.  In
this context, we propose a semi-supervised machine learning disambiguation
solution in the case large and partially annotated databases of scientific
publications. Using a real-world dataset of 1 million manual annotations, we
demonstrate how to exploit this data to learn an accurate classifier for
identifying corefering authors, to guide the clustering of scientific
publications by distinct authors in a semi-supervised way and finally to match
the resulting clusters with existing profiles.  Our analysis of parameters and
features reveal that... \glnote{To be completed with actual results.}
